MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-25 paper.Rmd
Better description of PFUSetup in the table.

| Package | Purpose |
|:--------|:--------|
| [IEATools][link-ieatools]             | Converts IEA data to [matsindf][link-matsindf] format |
| [MWTools][link-mwtools]               | Converts [ILO][link-ilo] and [FAO][link-fao] data to human and animal muscle work in [matsindf][link-matsindf] format |
| [Recca][link-recca]                   | Performs `R` energy conversion chain analysis |
| [PFUSetup][link-pfusetup]             | Setup for the [PFUDatabase][link-pfudatabase] and [PFUAggDatabase][link-pfuaggdatabase] pipelines |
| [PFUDatabase][link-pfudatabase]       | A [targets][link-targets] pipeline to create a data frame of PSUT matrices |
| [PFUAggDatabase][link-pfuaggdatabase] | A [targets][link-targets] pipeline to aggregate PSUT matrices |

>>>>

| Package | Purpose |
|:--------|:--------|
| [IEATools][link-ieatools]             | Converts IEA data to [matsindf][link-matsindf] format |
| [MWTools][link-mwtools]               | Converts [ILO][link-ilo] and [FAO][link-fao] data to human and animal muscle work in [matsindf][link-matsindf] format |
| [Recca][link-recca]                   | Performs `R` energy conversion chain analysis |
| [PFUSetup][link-pfusetup]             | Establishes input and output locations for the [PFUDatabase][link-pfudatabase] and [PFUAggDatabase][link-pfuaggdatabase] pipelines |
| [PFUDatabase][link-pfudatabase]       | A [targets][link-targets] pipeline to create a data frame of PSUT matrices |
| [PFUAggDatabase][link-pfuaggdatabase] | A [targets][link-targets] pipeline to aggregate PSUT matrices |
